---
title: "p8105_hw1_NL2836"
author: "Ngan Le"
date: "2023-09-23"
output: github_document
---

# Problem 1

First, we load the necessary libraries.

```{r setup, message = FALSE}
library(moderndive)
library(tidyverse)
```

This code chunk below downloads the dataset and views it.

```{r load dataset}
data("early_january_weather")
view(early_january_weather)
```

## a) Dataset short description

- This dataset includes information about the weather in early January of EWR in 2013. 

- The dataset has `r ncol(early_january_weather)` columns (i.e., variables), including `origin`, `year`, `month`, `day`, `hour`, `temp`, `dewp`, `humid`, `wind_dir`, `wind_speed`, `wind_gust`, `precip`, `pressure`, `visistb`, and `time_hour`. There are `r nrow(early_january_weather)` rows, or `r nrow(early_january_weather)` observations.

- The mean temperature is `r round(mean(early_january_weather$temp),1)`.

## b) Scatterplots

- This code chunk makes a scatterplot of `temp` (y) vs `time_hour` (x) with color points using the `humid` variable and print the plot.

```{r scatterplot temp/time_hour}
scatterplot_jan <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
print(scatterplot_jan)
```

### Describe plot pattern
- In EWR, the temperature (y axis) fluctuates between around 24F to around 58F during the first 15 days (x axis) of January in 2013. The humidity (color of the points) fluctuates from 30% to 100%. The 14th was the warmest day with high humidity. 

### Export scatterplot

This code chunk export the scatterplot to the project directory.

```{r export plot}
ggsave("scatterplot_jan.png", width = 5, height = 5, dpi = 300)
```


# Problem 2

## Create a dataframe with:
- Random sample of size 10, standard Normal Distribution. 
- Logical vector to indicate whether elements of the sample > 0.
- A character vector of length 10.
- A factor vector of length 10, with 3 different factor "levels".

This code chunk creates the dataframe accordingly and view it. 

```{r create dataframe}
random_df = tibble(
  sample = rnorm(10, mean = 0, sd = 1),
  log_vec = sample > 0,
  char_vec = c("a","b","c","d","e","f","g","h","i","j"),
  fac_vec = factor(
    sample(c("Group 1", "Level 2", "Level 3"), size = 10, replace = TRUE),
)
)

view(random_df)
```

## Take the mean of the variables

First take the mean of the variable `sample` in the dataframe and print it.

```{r}
mean(random_df$sample)
```

Next take the mean of the logical vector `log_vec` in the dataframe and print it.

```{r}
mean(random_df$log_vec)
```

Next take the mean of the character vector `char_vec` in the dataframe and print it.

```{r}
mean(random_df$char_vec)
```

Next take the mean of the factor vector `fac_vec` in the dataframe and print it.

```{r}
mean(random_df$fac_vec)
```

### Description
- Only the mean of the `sample` and the `log_vec` variables can be determined. 
- The mean of the `fac_vec` and `log_vec` cannot be determined since they are not numerical values.

## Convert the variables with `as.numeric`

`eval = FALSE` is used to specify no output of the code chunks when rendering the document.

### Convert `log_vec`

```{r convert log, eval = FALSE}
as.numeric(random_df$log_vec)
```

Here the `FALSE` values are converted into 0 and the `TRUE`values are converted into 1.

### Convert `char_vec`

```{r convert char, eval = FALSE}
as.numeric(random_df$char_vec)
```

Here the output is converted to `NA` (i.e., non applicable) because of coercion. This is because there is no numeric value assigned for any character value.

### Convert `fac_vec`

```{r convert fac, eval = FALSE}
as.numeric(random_df$fac_vec)
```

Here the `fac_vec` values are converted into numerical values according to their "levels". This is because factor vector are categorical data, and R determines the "levels" automatically based on the unique value of the factor vector. `Group A` is converted to 1, `Group B` is converted to 2, and `Group C` is converted to 3.





