---
title: "p8105_hw1_NL2836"
author: "Ngan Le"
date: "2023-09-23"
output: github_document
---

# Problem 1

First, we load the necessary libraries.

```{r setup}
library(moderndive)
library(tidyverse)
```

This code chunk below downloads the dataset and views it.

```{r load dataset}
data("early_january_weather")
view(early_january_weather)
```

## Dataset short description:

- This dataset includes information about the weather in early January of EWR in 2013. 

- The dataframe has `r ncol(early_january_weather)` columns (i.e., variables), including `origin`, `year`, `month`, `day`, `hour`, `temp`, `dewp`, `humid`, `wind_dir`, `wind_speed`, `wind_gust`, `precip`, `pressure`, `visistb`, and `time_hour`. There are `r nrow(early_january_weather)` rows, or `r nrow(early_january_weather)` observations.

- The mean temperature is `r round(mean(early_january_weather$temp),1)`.

## Scatterplots

- This code chunk makes a scatterplot of `temp` (y) vs `time_hour` (x) with color points using the `humid` variable.



